---
title: "test"
output:
  bookdown::html_document2: default
  html_document: default
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  comment = "#>"
)
```

```{r}
# library(kableExtra)
library(dplyr)
```

```{=latex}
\begin{tabular}{ll}
A & B \\
A & B \\
\end{tabular}
```

test123
45


The general form of a two-by-two table is shown in \@ref(tab:df-print)

|               | Event | Non-Event | Total
|-------------- | ------ | ---------- | ----- 
|Exposed        | a      | b | a+b
|Non-exposed    | c      | d | c+d
|Total         | a+c   | b+d | a+b+c+d

: A generic 2x2 table (\#tab:df-print)

this is a test \@ref(tab:df).

Table: (\#tab:df) The possible values of the `df_print` option for the `html_document` format.

| Option  | Description  |
|------------|-------------------------------------------|
| default  | Call the `print.data.frame` generic method |
| kable  | Use the `knitr::kable` function |
| tibble  | Use the `tibble::print.tbl_df` function |
| paged  |  Use `rmarkdown::paged_table` to create a pageable table |
| A custom function | Use the function to create the table |

See Table \@ref(tab:mtcars)

```{r mtcars}
knitr::kable(mtcars[1:5, 1:5], caption = "A caption")
```