---
title: "Example"
format: 
  html:
    filters:
     - at: post-quarto
       path: appendix_numbering.lua
    number-sections: false

crossref: 
  appendix-title: "Banana"
  custom:
    - kind: float
      key: suppfig
      reference-prefix: Supplementary Figure S
      space-before-numbering: false
    - kind: float
      key: supptab
      reference-prefix: Supplementary Table S
      space-before-numbering: false

---

# Main Body

## Another Section {#sec-main-1}

See also @sec-main-1, @sec-app1, @suppfig-banana, @supptab-apple, [Supplemental Tables S -@supptab-apple] and @sec-apx-two

# Appendix {.appendix}

## Appendix Section {.appendix #sec-app1}

Something here.

## Appendix Section {#sec-apx-two .appendix}

Content for the appendix.


::: {#suppfig-banana}

```{r}
plot(1:10)
```

Figure caption

:::

# Appendix 2 {.appendix}

::: {#supptab-apple}

```{r}
head(iris)
```

head of iris

:::

::: {#supptab-orange tbl-subcap=true}

windup

```{r}
head(iris)
```

## head of iris

```{r}
tail(iris)
```

## tail of iris

all of iris

:::
